Open-Vocabulary Semantic Parsing\\with both Distributional Statistics and Formal Knowledge

### 2016-03-18 papers/acl2016/paper.tex

    \path[]
      (1) edge node [sloped, anchor=center, above] {\formalpredicate{nationality}} (2)
      (1) edge node [sloped, anchor=center, above] {\formalpredicate{type}} (3)
      (1) edge node [sloped, anchor=center, above] {\formalpredicate{designed}} (5)
      (2) edge node [sloped, anchor=center, above] {\formalpredicate{type}} (4)
      (5) edge node [sloped, anchor=center, above] {\formalpredicate{located\_in}} (2);
  \end{tikzpicture}
  }
  \textbf{Features between \entity{Palladio} and \entity{Italy}}:\\
  \textless\formalpredicate{nationality}\textgreater\\
  \textless\formalpredicate{designed}, \formalpredicate{located\_in}\textgreater

  \textbf{Features for \entity{Palladio}}:\\
  \textless\formalpredicate{nationality}\textgreater\\
  \textless\formalpredicate{nationality}\textgreater:\entity{Italy}\\
  \textless\formalpredicate{type}\textgreater:\entity{Architect}\\
  \textless\formalpredicate{designed}, \formalpredicate{located\_in}\textgreater \\
  \textless\formalpredicate{designed}, \formalpredicate{located\_in}\textgreater:\entity{Italy}

  \caption{A subset of the Freebase graph, and some example extracted features
  between \entity{Palladio} and \entity{Italy}.  The actual Freebase relations
  and entity identifiers used are modified here to aid readability.}
  \label{fig:sfe}
\end{figure}

Subgraph feature extraction (SFE) is a technique introduced by Gardner and
Mitchell~\shortcite{gardner-2015-sfe} for generating feature matrices over node
pairs in a graph with labeled edges.  Given a pair of nodes in a graph, SFE
performs a search to characterize a subgraph around those two nodes, then
extracts various kinds of features from that subgraph, such as the set of edge
sequences that connect the two nodes.  \figref{sfe} shows an example subgraph,
centered around \entity{Andrea Pallado} and \entity{Italy}, and features that
would be extracted for that entity pair.  Gardner and Mitchell used these
features to perform link prediction in the graph, using characteristics of the
subgraph around two nodes to determine if an edge of a particular type should
exist between those nodes.\footnote{When the graph corresponds to a knowledge
base like Freebase, this task is also known as knowledge base completion.}
Gardner and Mitchell only used these features to model formal KB relations,
however.

We differ from the work done by Gardner and Mitchell in two ways.  First, we
apply these features to models of natural language, instead of formal KB
relations.  There are some non-trivial problems that need to be solved in order
to make this work, which will be discussed in \secref{method}.  Second, Gardner
and Mitchell only considered generating feature matrices over node \emph{pairs}
in a graph, with which one can model binary relations.  The natural language
queries we wish to answer also involve unary predicates, or categories.  We
thus extend SFE to also generate feature matrices over \emph{nodes} in a graph,
an extension that is straightforward and is also discussed in more detail in
\secref{method}.

@@

We use the dataset introduced by Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary},
which consists of the ClueWeb09 web
corpus\footnote{http://www.lemuproject.org/clueweb09.php} along with
Google's FACC entity linking of that corpus to
Freebase~\cite{gabrilovich-2013-clueweb-entity-linking}.  For training
data, 3 million webpages from this corpus were processed with a CCG
parser to produce logical forms.  This produced 2.1m predicate
instances involving 142k entity pairs and 184k entities.  After
removing infrequently-seen predicates (seen fewer than 6 times), there
were 25k categories and 4.2k relations.  The differences in numbers
reported here versus those reported by Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary} are
due to our improved logical form generation, discussed in
\secref{better-lfs}.

We also used the test set created by Krishnamurthy and Mitchell, which
contains 220 queries generated in the same fashion as the training
data from a separate section of ClueWeb.  However, as they did not
release a development set in with their data, we used this set as a
development set.  For a final evaluation, we generated another,
similar test set from a different held out section of ClueWeb, in the
same fashion as done by Krishnamurthy and Mitchell.  This final test
set contains 307 queries.  We report results on both of these test
sets below.

>>>>

    \path[]
      (1) edge node [sloped, anchor=center, above] {\formalpredicate{nationality}} (2)
      (1) edge node [sloped, anchor=center, above] {\formalpredicate{type}} (3)
      (1) edge node [sloped, anchor=center, above] {\formalpredicate{designed}} (5)
      (2) edge node [sloped, anchor=center, above] {\formalpredicate{type}} (4)
      (5) edge node [sloped, anchor=center, above] {\formalpredicate{located\_in}} (2);
  \end{tikzpicture}
  }
  \textbf{Features between \entity{Palladio} and \entity{Italy}}:\\
  \textless\formalpredicate{nationality}\textgreater\\
  \textless\formalpredicate{designed}$\rightarrow$\formalpredicate{located\_in}\textgreater

  \textbf{Features for \entity{Palladio}}:\\
  \textless\formalpredicate{nationality}\textgreater\\
  \textless\formalpredicate{nationality}\textgreater:\entity{Italy}\\
  \textless\formalpredicate{type}\textgreater:\entity{Architect}\\
  \textless\formalpredicate{designed}$\rightarrow$\formalpredicate{located\_in}\textgreater \\
  \textless\formalpredicate{designed}$\rightarrow$\formalpredicate{located\_in}\textgreater:\entity{Italy}

  \caption{A subset of the Freebase graph, and some example extracted
  features.  The actual Freebase relations and entity identifiers used
  are modified here to aid readability.}
  \label{fig:sfe}
\end{figure}

Subgraph feature extraction (SFE) is a technique introduced by Gardner
and Mitchell~\shortcite{gardner-2015-sfe} for generating feature
matrices over node pairs in a graph with labeled edges.  Given a pair
of nodes in a graph, SFE performs a search to characterize and extract
features from a subgraph around those two nodes.  Example features
include the set of edge sequences that connect the two nodes.
\figref{sfe} shows an example subgraph for the pair \entity{Andrea
Pallado} and \entity{Italy}, and features that would be extracted for
that entity pair.  Gardner and Mitchell used these features to perform
link prediction in the graph, using characteristics of the subgraph
around two nodes to determine if an edge of a particular type should
exist between those nodes.\footnote{When the graph corresponds to a
knowledge base like Freebase, this task is also known as knowledge
base completion.}

We differ from the work done by Gardner and Mitchell in two ways.
First, we apply these features to models of natural language, instead
of to the link prediction task.  Second, Gardner and Mitchell only
considered generating feature matrices over node \emph{pairs} in a
graph, with which one can model binary relations.  The natural
language queries we wish to answer also involve unary predicates.  We
thus extend SFE to also generate feature matrices over \emph{nodes} in
a graph, a straightforward extension that is described in
\secref{method}.

@@

We use the dataset introduced by Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary},
which consists of the ClueWeb09 web
corpus\footnote{http://www.lemuproject.org/clueweb09.php} along with
Google's FACC entity linking of that corpus to
Freebase~\cite{gabrilovich-2013-clueweb-entity-linking}.  For training
data, 3 million webpages from this corpus were processed with a CCG
parser to produce logical forms~\cite{krishnamurthy-2014-joint-ccg}.
This produced 2.1m predicate instances involving 142k entity pairs and
184k entities.  After removing infrequently-seen predicates (seen
fewer than 6 times), there were 25k categories and 4.2k relations.
The differences in numbers reported here versus those reported by
Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary} are
due to our improved logical form generation, discussed in
\secref{better-lfs}.

We also used the test set created by Krishnamurthy and Mitchell, which
contains 220 queries generated in the same fashion as the training
data from a separate section of ClueWeb.  However, as they did not
release a development set in with their data, we used this set as a
development set.  For a final evaluation, we generated another,
similar test set from a different held out section of ClueWeb, in the
same fashion as done by Krishnamurthy and Mitchell.  This final test
set contains 307 queries.  We report results on both of these sets
below.
